Towards multiversal modal operators for homotopy type theory

### 2023-11-29 slides-hottest2023.tex
First slide finished

  \textbf{Examples.} (classically)\ $(\NN,{\leq}),\ \ X \times Y,\ \ X^*,\ \ \mathrm{Tree}(X).$
  \medskip
  \pause

  \subhead{\emph{A naive formalization attempt}}

  \textbf{Def.} $\mathsf{Well}(X,{\leq}) \defeq
    \prod\limits_{\alpha \? \NN \to X} \, \Bigl\|\sum\limits_{i \? \NN} \sum\limits_{j \? \NN}
      i < j \times \alpha(i) \leq \alpha(j)\Bigr\|_{-1}$
  \pause

  \begin{multicols}{2}
  \begin{itemize}
    \item[\cmark] short
    \item[\cmark] sweet
    \item[\cmark] immediate
    \columnbreak
    \item[\xmark] philosophically strenuous  %: needless reference of the transfinite
    \item[\xmark] not practical  %: cannot verify closure properties
    \item[\xmark] not faithful(?)  %: missing out on some sequences
  \end{itemize}
  \end{multicols}
\end{frame}}

>>>>

  \textbf{Examples.} (classically)\ $(\NN,{\leq}),\ \ X \times Y,\ \ X^*,\ \ \mathrm{Tree}(X).$
  \bigskip
  \pause

  %\subhead{\emph{A naive formalization attempt}}
  \emph{A naive formalization attempt:}

  \textbf{Def.} $\displaystyle\mathsf{Well}(X,{\leq}) \defeq
    \prod\limits_{\alpha \? \NN \to X} \, \Bigl\|\sum\limits_{i \? \NN} \sum\limits_{j \? \NN}
      i < j \times \alpha(i) \leq \alpha(j)\Bigr\|_{-1}$
  \pause
  \qquad\scalebox{2}{\dbend}
  \medskip

  \begin{itemize}
    \item[\bad{\xmark}] philosophically~strenuous  %: needless reference of the transfinite
    \item[\bad{\xmark}] not practical  %: cannot verify closure properties
    \item[\bad{\xmark}] not faithful(?)  %: missing out on some sequences
  \end{itemize}
\end{frame}}
